---
title: "Get Location Information from the Description"
author: "Benjamin Sinturel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Location Information from the Description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

When we receive the dataframe of every ads description, we clean the dataframe to get descriptions in lower characters and without any accent,faulty character or any punctuation. 

```{r}
#clean(annonces)
```

- If we want to know if a place is present in a description text, match_environnement match places from a dataframe of roads,streets or tube stations with a dataset of ads descriptions. This example takes roads into account. 

```{r}
#match_environnement <- function("rue de montreuil","extrait de la derniere description au 97 rue de montreuil dans un bel immeuble")
```

- If we want to know if a place is present in a description text, match_environnement match places from a dataframe of roads,streets or tube stations with a dataset of ads descriptions. This example takes tube stations into account. 

```{r}
#match_environnement <- function("metro passy","extrait de la derniere description au 4 rue de l'abbe gillet metro passy")
```

-If an ads description contains a street, we use number to get the number of the street if available by taking the number in front of the word "rue" (street in french) in the description. 

```{r}
#number <- function(castorus)
```

-After collecting the extracted information we combines them with the information already present in the data scrapping. 
In this dataframe we give priority to the data already present from the data scrapping. When this one returns an NA, we fill the void thanks to the extracted data. 

```{r}
#combine_roads <- function(castorus,roadnames,metros)
```











